Mapping Properties of Surface Source Extension

### 2025-08-06 repro/papers/ssefound/paper.tex
minor

@@

Define
\[
  F = \phi_r S(T) \phi_s
\]
in which $\phi_,r \in C_0^{\infty}(\bR^{n+1})$ and $T>0$. Suppose that $K$
is perturbed by $\delta K \in OPS^1$, also essentially skew. Then
$\Lambda$, $U$, $S$, $\tilde{S}$ and $F$ undergo perturbations
$\delta \Lambda$, $\delta U$, $\delta S$, $\delta \tilde{S}$, and
$\delta F$. Our object is to understand the structure of $\delta F$, under the
assumption that $\phi_r \delta K \in OPS^{-\infty}$.

This assumption on $\delta K$ implies that $\phi_r \delta U \in
OPS^{-\infty}$. 
\[
  \delta F =  \phi_r \delta S(T)  = \phi_r \left(\sum _{j=1}^k \delta U_j \tilde{S}_j(T) U_j^*
\right.
\]
\[
 +  \left. \sum_{j=1}^k U_j \delta\tilde{S}_j(T)U_j^* + \sum_{J=1}^k U_j
    \tilde{S}_j(T)\delta U_j^*\right) 
\]
Every term in the first sum on the RHS is bounded $H^s \rightarrow H^{s-1}$ since
$\phi_r \delta U_i \in OPS^{-\infty}$.  Since $[\phi_rU_i], \in OPS^{-1}$, 
\[
  \phi_r  U_j \delta \tilde{S}_j(T)  U_j^*  = U_j \phi_r
  \tilde{S}_j(T) U_j^*
  +...
\]
where the elided terms are operators mapping $H^s$ to $H^{s-1}$, any
$s$. So,
\[
 \delta F = \sum_{j=1}^k U_j \phi_r \left( \delta\tilde{S}_j(T) U_i^*
   + \tilde{S}_j(T) \delta U_j^*\right)
  + ...
\]
and
\[
 S(-T)\delta F =\left(\sum_{i=1}^k U_i \tilde{S}_i(T)
    U_i^*\right) \left(\sum_{j=1}^k U_j \phi_r ( \delta\tilde{S}_j(T) U_i^*
    + \tilde{S}_j(T) \delta U_j^*)\right)
\]  
Using the relation \ref{eqn:ortho},
The first order perturbation of the definition \ref{eqn:stilde} is
\begin{equation}
  \label{eqn:dstilde}
  \partial_t \delta \tilde{S}_i(t) = - i\lambda_i \delta
  \tilde{S}_i(t) - i\delta \lambda_i \tilde{S}_i(t)
\end{equation}
Since $\tilde{S_i}(-t)$ is inverse to $\tilde{S}_i(t)$,
\[
  \partial_t \tilde{S}_i(-t)= -\tilde{S}_i(-t) (\partial_t \tilde{S}_i(t)) \tilde{S}_i(-t)
\]
\begin{equation}
  \label{eqn:stildeinv}
= -\tilde{S}_i(-t)(-i\lambda_i \tilde{S}_i(t)) \tilde{S}_i(-t) = i\tilde{S}_i(-t)\lambda_i 
\end{equation}
So
%\[
% \partial_t (\tilde{S}_i(-t) \phi_r \delta \tilde{S}_i(t) \phi_s) 
%\]
%\[
%  = i\tilde{S}_i(-t)\lambda_i \phi_r \delta \tilde{S}_i(t) \phi_s +
%  \tilde{S}_i(-t) \phi_r (- i\lambda_i \delta
%  \tilde{S}_i(t) - i\delta \lambda_i \tilde{S}_i(t)) \phi_s
%\]
%\[
%  = -i\tilde{S}_i(-t)[\lambda_i,\phi_r] \delta \tilde{S}(t) \phi_s -i
%  \tilde{S}_i(-t)\phi_r\delta\lambda_i\tilde{S}_i(t) \phi_s
%\]
%\begin{equation}
%  \label{eqn:qevol1}
%  = -i\tilde{S}_i(-t)[\lambda_i,\phi_r]\tilde{S}_i(t) \tilde{S}_i(-t)\delta \tilde{S}(t) \phi_s %-i
%  \tilde{S}_i(-t)\phi_r\delta\lambda_i\tilde{S}_i(t) \phi_s.
%\end{equation}
%Similarly,
\begin{equation}
  \label{eqn:dstildeconj}
  \partial_t\tilde{S}_i(-t)\delta \tilde{S}_i(t) = -i\tilde{S}_i(-t)\delta \lambda_i \tilde{S}_i(t).
\end{equation}
From \cite{Tay:81}, Egorov's Theorem (Section VIII.1), for $p \in OPS^s(\bR^n)$,
\begin{equation}
  \label{eqn:egorov}
   \tilde{S}_i(-t) p \tilde{S}_i(t)=  p \circ C_i(t),\, p\tilde{S}_i(t) =
   \tilde{S}_i(t)p \circ C_i(t)
\end{equation}
in which $C_i$ is the one-paraimeter family of symplectic maps given by
\begin{equation}
  \label{eqn:canon}
  C_i(t)(x,\xi)=(y_i(t;x,\xi),\eta_i(t;x,\xi))
\end{equation}
Here $t \rightarrow y_i(t;x,\xi),\eta_i(t;x,\xi) $is the integral curve of the
Hamiltonian vector field
\[
  H_i(x,\xi) = (\partial_{\xi}\lambda_i(x,\xi), - \partial_x\lambda_i(x,\xi))
\]
with $y_i(0;x,\xi)=x, \eta_i(0;x,\xi)=\xi$.

>>>>

\section{Scalar $\Psi$DO evolution}

3D case: $\lambda(x,z,\xi,\eta) \in S^1(\bR^2) \subset
C^{\infty}(\bR,S^1(\bR^2))$ not a $\Psi$DO on $\bR^3$ however can make
one:

Suppose $H \in OPS^0(\bR^3)$ is convolution operator, $\phi \in
C^{\infty}_0(\bR^3)$. Let ${\cal N}_t = \{(t,x,z,\omega,\xi,\eta):
\xi=\eta=0\}$ be the normal bundle of the constant-$t$ foliation, and
suppose that $ES(H) \cap {\cal N}_t = \emptyset$. Then $p = \lambda \phi H
\in OPS^1(\bR^3)$,
\[
p(x,z,t,\xi,\zeta,\omega) = \left(\int d\xi' d\zeta'
\lambda(x,z,\xi+\xi',\zeta+\zeta'){\cal
  F}_{(x,z)}\phi(t,\xi',\zeta')\right)H(\xi,\zeta,\omega)
\]
Suppose $u \in H^s_{\rm loc}(\bR^3)$ satisfies $(\partial_t + i\lambda(x,z,\partial_x,\partial_z))u \in
H^s_{\rm loc}(\bR^3)$, and $(I-H)u \in H^{s+1}_{\rm loc}(\bR^3)$.
%Also
%choose $\phi_1 \in C^{\infty}_0(\bR^3)$ for which $\phi_1=1$ on
%$\mbox{supp }\phi$.
Then
\[
  p(x,z,t,\partial_x,\partial_z,\partial_t)u = \lambda \phi u \mbox{
    mod } H^{s}_{\rm loc}
\]
\[
  = \partial_t \phi u \mbox{ mod } H^{s}_{\rm loc}.
\]

@@

Define
\[
  F = \phi_r S(T) \phi_s
\]
in which $\phi_{s,r} \in C_0^{\infty}(\bR^{n+1})$ and $T>0$. Suppose that $K$
is perturbed by $\delta K \in OPS^1$, also essentially skew. Then
$\Lambda$, $U$, $S$, $\tilde{S}$ and $F$ undergo perturbations
$\delta \Lambda$, $\delta U$, $\delta S$, $\delta \tilde{S}$, and
$\delta F$. Our object is to understand the structure of $\delta F$, under the
assumption that $\phi_{s,r} \delta K \in OPS^{-\infty}$, i.e. that
$\delta K$ essentially vanishes on the supports of $\phi_{s,r}$.

This assumption on $\delta K$ implies that $\phi_{s,r} \delta U_i \in
OPS^{-\infty}, i=1,...,k$. 
\[
  \delta F =  \phi_r \delta S(T) \phi_s  = \phi_r \left(\sum _{j=1}^k \delta U_j \tilde{S}_j(T) U_j^*
\right.
\]
\[
 +  \left. \sum_{j=1}^k U_j \delta\tilde{S}_j(T)U_j^* + \sum_{J=1}^k U_j
    \tilde{S}_j(T)\delta U_j^*\right) \phi_s
\]
Every term in the first and last sums on the RHS is smoothing, since
$\phi_r \delta U_i, \delta U_i^* \phi_s\in OPS^{-\infty}$:
\[
  \delta F = \phi_r \left(\sum_{j=1}^k U_j
    \delta\tilde{S}_j(T)U_j^*\right)\phi_s \mbox{ mod }OPS^{-\infty}
\]
Denote by ${\cal B}$ operators on $H^{\infty}$ that are bounded on
each $H^s$, all $s \in \bR$ (so $OPS^0 \subset {\cal B}$

Since $[\phi_{s,r},U_i] \in OPS^{-1}$, this is
\[
  = \sum_{j=1}^k U_j \phi_r \delta \tilde{S}_j(T) U_J^*\phi_s 
  \mbox{ mod }{\cal B}
\]
and
\[
 S(-T)\delta F =\left(\sum_{i=1}^k U_i \tilde{S}_i(-T)
    U_i^*\right) \left(\sum_{j=1}^k U_j \phi_r (\delta\tilde{S}_j(T) U_j^*\phi_s\right)
\]
Using the relation \ref{eqn:ortho} and $\tilde{S}_i(-t)\tilde{S}_i(t)=I$, this is
\[
  = \left(\sum_{i=1}^k U_i \tilde{S}_i(-T) \phi_r \delta\tilde{S}_i(T) U_i^*\phi_s
)
\]
The first order perturbation of the definition \ref{eqn:stilde} is
\begin{equation}
  \label{eqn:dstilde}
  \partial_t \delta \tilde{S}_i(t) = - i\lambda_i \delta
  \tilde{S}_i(t) - i\delta \lambda_i \tilde{S}_i(t)
\end{equation}
Since $\tilde{S_i}(-t)$ is inverse to $\tilde{S}_i(t)$,
\[
  \partial_t \tilde{S}_i(-t)= -\tilde{S}_i(-t) (\partial_t \tilde{S}_i(t)) \tilde{S}_i(-t)
\]
\begin{equation}
  \label{eqn:stildeinv}
= -\tilde{S}_i(-t)(-i\lambda_i \tilde{S}_i(t)) \tilde{S}_i(-t) = i\tilde{S}_i(-t)\lambda_i 
\end{equation}
So
%\[
% \partial_t (\tilde{S}_i(-t) \phi_r \delta \tilde{S}_i(t) \phi_s) 
%\]
%\[
%  = i\tilde{S}_i(-t)\lambda_i \phi_r \delta \tilde{S}_i(t) \phi_s +
%  \tilde{S}_i(-t) \phi_r (- i\lambda_i \delta
%  \tilde{S}_i(t) - i\delta \lambda_i \tilde{S}_i(t)) \phi_s
%\]
%\[
%  = -i\tilde{S}_i(-t)[\lambda_i,\phi_r] \delta \tilde{S}(t) \phi_s -i
%  \tilde{S}_i(-t)\phi_r\delta\lambda_i\tilde{S}_i(t) \phi_s
%\]
%\begin{equation}
%  \label{eqn:qevol1}
%  = -i\tilde{S}_i(-t)[\lambda_i,\phi_r]\tilde{S}_i(t) \tilde{S}_i(-t)\delta \tilde{S}(t) \phi_s %-i
%  \tilde{S}_i(-t)\phi_r\delta\lambda_i\tilde{S}_i(t) \phi_s.
%\end{equation}
%Similarly,
\begin{equation}
  \label{eqn:dstildeconj}
  \partial_t\tilde{S}_i(-t)\delta \tilde{S}_i(t) = -i\tilde{S}_i(-t)\delta \lambda_i \tilde{S}_i(t).
\end{equation}
From \cite{Tay:81}, Egorov's Theorem (Section VIII.1), for $p \in OPS^s(\bR^n)$,
\begin{equation}
  \label{eqn:egorov}
   \tilde{S}_i(-t) p \tilde{S}_i(t)=  p \circ C_i(t),\, p\tilde{S}_i(t) =
   \tilde{S}_i(t)p \circ C_i(t)
\end{equation}
in which $C_i$ is the one-paraimeter family of symplectic maps given by
\begin{equation}
  \label{eqn:canon}
  C_i(t)(x,\xi)=(y_i(t;x,\xi),\eta_i(t;x,\xi))
\end{equation}
Here $t \rightarrow y_i(t;x,\xi),\eta_i(t;x,\xi) $is the integral curve of the
Hamiltonian vector field
\[
  H_i(x,\xi) = (\partial_{\xi}\lambda_i(x,\xi), - \partial_x\lambda_i(x,\xi))
\]
with $y_i(0;x,\xi)=x, \eta_i(0;x,\xi)=\xi$.
